Union and intersection contracts are hard, actually

### 2021-06-09 paper.tex
Small wording issue

In these practical gradual type systems the problem is to be able to
capture, in static types, as many programming patterns as possible
from the underlying dynamically typed language. One such pattern is
heterogeneous collections, in JavaScript (for TypeScript) and Python
(for MyPy), heterogeneous collections, say arrays with values of
different types, are frequent. For instance, in TypeScript, an array
which can contain both strings and numbers would have type
\typescript{Array<string|number>}.

>>>>

The problem that these practical gradual type systems are trying to solve is to
capture, in static types, as many programming patterns as possible
from the underlying dynamically typed language. One such pattern is
heterogeneous collections, in JavaScript (for TypeScript) and Python
(for MyPy), heterogeneous collections, say arrays with values of
different types, are frequent. For instance, in TypeScript, an array
which can contain both strings and numbers would have type
\typescript{Array<string|number>}.
